Millions of Type Errors

### 2023-09-01 programming23/paper.tex
dataset overview fig

\usepackage{alltt}
\usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{wasysym}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

"89.1417"
"10.4259"
"0.4323"

  %% TODO subfigure??
  \begin{tabular}{ll}
    \begin{tabular}{r@{~~}l@{~~}r}
       1,341,348 & \mnocheck{}          & [\pct{89.14}] \\
         156,883 & \mnonstrict{}        & [\pct{10.43}] \\
           6,505 & \mstrict{}           & [\pct{ 0.43}] \\\midrule
       1,504,736 & \zerowidth{Total telemetry records}
    \end{tabular}
    \begin{tabular}{r@{~~}l@{~~}r}
         508,572 & due to module switch & [\pct{33.80}] \\
         996,164 & due to keystrokes    & [\pct{66.20}]
    \end{tabular}
  \end{tabular}

 72,235,735 total forced strict type errors, 37,027,281 in module, 1,111,178 in edit regions

 595,137 total type errors, 289,698 in module, 14,917 non-stx + 16,007 syntax in edit regions

 347,598 sessions
  346,956 single mode = 313,509 nocheck + 32,902 nonstrict + 545 strict
  512 multi mode projects
  341 mode upgrades
  320 mode downgrades

%  \begin{tabular}{rl}
%   182,247 & total forced-strict type errors \\
%         & {83,005 in module, 5,113 in edit regions} \\
%    1,521 & total type errors \\
%         & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
%    \\[2ex]
%
%    1,146 & sessions \\
%    & \begin{tabular}{l}
%      1,143 single mode = 1046 \mnocheck{} + 94 \mnonstrict{} + 3 \mstrict{} \\
%        detected 2 multi-mode projects, 2 mode upgrades, 2 mode downgrades
%      \end{tabular}
%  \end{tabular}

>>>>

\usepackage{alltt}
\usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

FILL te in edit region, 
 14,917 non-stx
 16,007 syntax in edit regions.
 Most are typos!

\begin{figure}[t]
  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      \begin{tabular}[t]{r@{~~}l@{~~}r}
         1,341,348 & \mnocheck{}          & [\pct{89.14}] \\
           156,883 & \mnonstrict{}        & [\pct{10.43}] \\
             6,505 & \mstrict{}           & [\pct{ 0.43}]
      \end{tabular}
      \begin{tabular}[t]{r@{~~}l@{~~}r}
           508,572 & due to module switch & [\pct{33.80}] \\
           996,164 & due to keystrokes    & [\pct{66.20}]
      \end{tabular}
    \end{tabular}
    \caption{Total telemetry records (1,504,736), analysis modes, and reason-for-sending}
    \label{f:total-records}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      \begin{tabular}[t]{lrl}
        595,137 & Type errors \\
        289,698 & in current module & [\pct{48.68}] \\
         30,924 & in edit region & [\pct{5.20}]
      \end{tabular}
      \begin{tabular}[t]{lrl}
        72,235,735 & {Forced-strict errors} \\
        37,027,281 & in current module & [\pct{51.26}] \\
         1,111,178 & in edit region & [\pct{1.54}]
      \end{tabular}
    \end{tabular}
    \caption{Type errors and forced-strict errors across all telemetry records}
    \label{f:total-tefs}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      \begin{tabular}[t]{lrl}
        313,509 & \mnocheck{}   & [\pct{90.19}] \\
         32,902 & \mnonstrict{} & [\pct{ 9.47}] \\
            545 & \mstrict{}    & [\pct{ 0.16}] \\
            642 & mixed-mode    & [\pct{ 0.18}]
      \end{tabular}
      \begin{tabular}[t]{l@{~~}ll}
        \zerowidth{Among the mixed-mode sessions:} \\
        & 341 & contain a mode upgrade \\
        & 320 & contain a mode downgrade \\
        & 512 & contain modules with different modes
      \end{tabular}
    \end{tabular}
    \caption{Total sessions (347,598), whether/how they switch analysis mode}
    \label{f:total-sessions}
  \end{subfigure}
